---
output: 
  html_document:
    include:
     after_body: footer.html
knit: (function(inputFile, encoding) { out_dir <- 'docs'; rmarkdown::render(inputFile, encoding=encoding, output_file=file.path(dirname(inputFile), out_dir, 'index.html')) })
---
<style>
.main-container {
    max-width: 1200px;
    margin-left: 20;
    margin-right: auto;
}
</style>

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE)
```
###  Index of Anchiq verbs and their inflectional properties {.tabset .tabset-fade .tabset-pills}

Download the database of Anchiq verbs: [.csv](https://raw.githubusercontent.com/triolo/anchiq-verb-index/master/idxrsort.csv)

#### About the index
This index contains 200 Anchiq verb roots and some information on their inflectional properties.


The columns of the index indicate the following information:

-   **Id** — identificator of a root, retained for the sake of compatibility with printed index.

-   **Label** — a lexical label of a verb

-   **Translation** - russian translation of a lexical label

-   **Root** - a root of a verb in ist underlying form

-	  **Slot** - presence of class agreement clot --- indicates whether a verb can agree with its absolutive argument

-   **Conj** - conjugation type: *A*, *E* or *U*.

-	  **Nas** - indicates if a verb is mophophonologically nasalized

-   **Lab** - indicates if a verb is mophophonologically labialized, +Lp stands for parasytic labialization, +Lr stands for robust labialization of velars, uvulars and laryngeals

-	  **Son** - indicates, whether a verb has a mophophonologically sonorant auslaut

-	  **Defic** - paradigm deficiency type: *Norm* means non-deficient paradigm, *Incr* denotes that a verb can attach only causativized (increased) morphology, *Std* denotes that a verb can attach only non-causativized (standard) morphology

-	  **Irreg** - contains all known paradigm irregularities: *AltIPFV* means that a verb chooses an alternative set of imperfective morphology, *AddIPFV* means that a verb has an additional form of imperfective in analytic paradigm. 


#### Search

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 9.5}
library(DT)
library(tidyverse)
library(dplyr)
dtable = read.csv("idxrsort.csv") 
datatable(dtable, filter = list(position = 'top', clear = FALSE, plain = TRUE), rownames = FALSE,  extensions = 'Buttons', options = list(pageLength = 20, dom = 'Bfrtip' , buttons = I('colvis'),autoWidth = TRUE), escape = FALSE) 
```

